The Astropy Project: Building an inclusive, open science project and status of the v2.0 software

### 2018-01-05 main.tex
; -> .

An example of a visualization made with \package{wcsaxes} is shown in
\figurename~\ref{fig:wcsaxes}; This example illustrates the ability to
overlay multiple coordinate systems and customize which ticks/labels are shown
on which axes around the image. This also uses the image stretching
functionality from \sectionname~\ref{sec:stretch} to show the image in a
square-root stretch (automatically updating the tick positions in the colorbar).

>>>>

An example of a visualization made with \package{wcsaxes} is shown in
\figurename~\ref{fig:wcsaxes}. This example illustrates the ability to
overlay multiple coordinate systems and customize which ticks/labels are shown
on which axes around the image. This also uses the image stretching
functionality from \sectionname~\ref{sec:stretch} to show the image in a
square-root stretch (automatically updating the tick positions in the colorbar).
